Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-04-14 draft/paper1.tex
Add Komiyama-san to author list

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH

@@

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        Yen-Ting Lin,$^{5}$
        \newauthor
        Masayuki Tanaka,$^{6}$
        Rachel Mandelbaum,$^{7}$
        Satoshi Miyazaki,$^{5,8}$
        HSC collaboration 
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    Following an initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
    massive galaxies and a large fraction of these massive progenitors become quiescent 
    at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase in the ``two-phase'' formation scenario is driven by 
    non-dissipative processes such as dry mergers with other galaxies 
    (e.g. \citealt{Naab2006, Khochfar2006}). 
    According to the ``two-phase'' scenario, minor mergers drive the growth of massive 
    galaxies at late times and can help explain the significant increase
    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) as well as the build-up 
    of the outer stellar halos of ETGs (e.g.  \citealt{Szomoru2012, Patel2013}).

    {\bf PP here about mass dependence: in the simulations, a larger fraction of the mass 
    is ex-situ at increasingly higher mass. Can we see evidence for that observationally by 
    looking at light profiles?}

    In addition, according to this two-phase formation scenario, the late time growth of massive ETGs 
    is intrinsically tied to the growth of their host dark matter halos 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs that live at the center of more massive halos should experience 
    a different mass assembly history and should be subject to a larger merger rate 
    compared to ETGs that live in smaller dark matter halos. 
    A natural prediction of the two-phase formation scenario is therefore that the 
    structural properties of massive galaxies should depend on their ``environment''

@@

    In this paper, we take advantage of new high-resolution (median 
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
    as a function of their properties. Here we will focus on (a) showing that we can 
    measure profiles for galaxies out to 100 kpc reliably with the HSC data and (b) looking at 
    trends in stellar mass and outer envelope properties. In a second paper in this series, we 
    will directly show the environmental dependence of the outer envelope mass.
    %The goal of this paper is to compare the \mden{} profiles and structural scaling 
    %relations of massive central galaxies in both low and high mass dark matter halos. 
    %Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
    %ETGs using SDSS versus using the new HSC data. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
    select a large sample (${\sim} 15000$) of massive central 
    galaxies with $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
    HSC wide layer.

    Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
    providing appropriate model to describe the \mstar{} distribution of massive 
    galaxy from its center to the very outskirt, we focus on \mstar{} within two 
    different physical apertures in this work:

        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
            builds up the inner, dense core of massive ETGs.  
            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
            We use \minn{} as a proxy for the mass forged during the ``in-situ''
            phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over our 
            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
            0.3 and 0.5).

       \end{itemize}
%% ------------------------------------------------------------------------------------ %%

    {\bf We will show the implications for the stellar mass function of including most of 
    the stellar light, a task that has been complicated before now due to shallower data. 
    We will also investigate the idea that the accreted fraction is a function of stellar mass.}

@@

    We begin by using a broad luminosity cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on \citep{Leauthaud2016}, galaxies with \logms{}$\geq 11.5$ mostly have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
    We therefore select our initial sample to be brighter than 
    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences between 
    the response curves of SDSS-$i$ and HSC-$i$ filters.}
    and also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in the $i$-band.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We further select extended objects with no deblending errors, with well defined 
    centroids, and with \texttt{cModel} magnitudes in all five bands. 
    After removing objects that have pixels affected by saturation, cosmic-rays, or 
    other optical artifacts\footnote{each criterion removes less than 8\% of the 
    entire sample.}.This sample corresponds to 1760845 galaxies and will be referred 
    as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

@@

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (will be referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
    spec-$z$. 
    By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
    our \texttt{hscZ} sample by 14\%. 
    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z{\sim} 0.5$. 
    We can therefore expect our sample to be roughly \mstar{}-complete above 
    \logms{}$\geq 11.5$-$11.6$. 
    This question will be addressed more carefully using the overlap region between 
    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
    {\bf Seems to have the section wrong? Plus, can we consolidate these discussions?}

%% ------------------------------------------------------------------------------------ %%  
\subsection{The \redm{}{} cluster catalog}
    \label{ssec:redmapper}

    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
    The \redm{} catalog therefore helps us group massive central galaxies into 
    samples with different average \mhalo{}. 
    We will use the central galaxies of \redm{} clusters 
    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
    live in massive halos.
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{Massive Central Galaxies in Low and High Mass Halos}
    \label{ssec:mass_central}

    One of the goals of our work is to investigate the halo dependence of the outer 
    envelope. Although there is a correlation between $M_{\star}$ and $M_{\mathrm{Halo}}$,
    based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
    With the help of the \redm{} catalog, we can broadly separate our sample into two
    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
    live in a fairly broad range of halos masses.

    We match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
    galaxies at $0.3 \leq z \leq 0.5$.
    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
    as the \rbcg{} sample. 
    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
    ${\sim} 41$, corresponding to halo mass of 
    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
    %% Saved as "dr1_redbcg_use_sed5b.fits"

    Out next goal is to construct a sample of central galaxies living in halos with 
    \logmh{}$<14.0$. 
    We first identify and remove all galaxies within a cylindrical region around all 
    \redm{} clusters. 
    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
    set to twice the uncertainty of the photometric redshift error. 
    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
    \citet{Simet2016} and we use the mass-concentration relation from 
    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
    cluster members.
    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
    in our sample will be dominated by central galaxies living in halos with 
    \logmh{}$\leq 14.0$. 
    We will refer to this sample of \textbf{central galaxies in less massive halos}
    as the \nbcg{} sample.

    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
    To ensure a clean separation in \mhalo{}, here we only focus on the central 
    galaxies of clusters with $\lambda > 30$. 
    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
    We have checked that none of the results in this work depend on the choice of this 
    $\lambda$ limit. 
    For massive central galaxies that are not in these cluster-level halos, 
    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
    {\bf I am still a bit confused why stellar mass completeness depends on Mh??}

    We note that at this stage, our \nbcg{} sample still contains galaxies with a 
    wide range of \mstar{} values. 
    Later on, once we have more accurate \mstar{} estimates, we will further limit this 
    sample to \logms{}$ > 11.5$. 
    At this very high mass end, and given that we have rejected satellites in \redm{} 
    clusters, any further satellite contamination can be safely neglected 
    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
    %% Saved as "dr1_nonbcg_use_sed5b.fits"
    % TODO: The actual number waits to be updated}

@@

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
            with reliable redshift information. 
        \item {\bf Select only central galaxies using RedMapper: total number in full 
        sample?}
        \item We further divide the sample into an \rbcg{} sample and a \nbcg{} sample, 
          with the former roughly having \logmh{}$\geq 14.2$ and the latter having 
           \logmh{}$<14.0$.

    We now proceed to measure the luminosities and stellar mass profiles for 
    all galaxies in the \rbcg{} and \nbcg{} samples.
%% ------------------------------------------------------------------------------------ %%

>>>>

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH
% Version 6; MNRAS format; Paper I edited by JG

@@

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny E. Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        Yen-Ting Lin,$^{5}$
        \newauthor
        Masayuki Tanaka,$^{6}$
        Rachel Mandelbaum,$^{7}$
        Satoshi Miyazaki,$^{5,8}$
        Yutaka Komiyama,$^{5,8}$
        HSC collaboration 
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    Following this initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
    massive galaxies and a large fraction of these massive progenitors become quiescent 
    at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase in the ``two-phase'' formation scenario is driven by 
    non-dissipative processes such as dry mergers with other galaxies 
    (e.g. \citealt{Naab2006, Khochfar2006}). 
    According to the ``two-phase'' scenario, minor mergers drive the growth of massive 
    galaxies at late times and can help explain the significant increase
    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) as well as the build-up 
    of the outer stellar halos of ETGs (e.g.  \citealt{Szomoru2012, Patel2013}).        
    {\bf Words here about mass dependence: in the simulations, a larger fraction of the mass 
    is ex-situ at increasingly higher mass. Seen in early work by Naab, Oser, etc, and in the 
    Illustris papers. First prediction to compare with is that the accreted/ex-situ fraction is 
    a function of mass.}

    In addition, according to this two-phase formation scenario, the late time growth of massive ETGs 
    is intrinsically tied to the growth of their host dark matter halos 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs that live at the center of more massive halos should experience 
    a different mass assembly history and should be subject to a larger merger rate 
    compared to ETGs that live in smaller dark matter halos. 
    A second prediction of the two-phase formation scenario is therefore that the 
    structural properties of massive galaxies should depend on their ``environment''

@@

    In this paper, we take advantage of new high-resolution (median 
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
    as a function of their properties. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
    select a large sample (${\sim} 15000$) of massive central 
    galaxies with $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
    HSC wide layer. In this paper, we use this sample to (a)  
    measure profiles for galaxies out to 100 kpc reliably with the HSC data and (b) examine the implications 
    for the stellar mass function when the outer parts of galaxies are accounted for (c) look at 
    trends in outer envelope properties as a function of stellar mass. In a second paper in this series, we 
    will directly show the environmental dependence of the outer envelope mass.
    %The goal of this paper is to compare the \mden{} profiles and structural scaling 
    %relations of massive central galaxies in both low and high mass dark matter halos. 
    %Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
    %ETGs using SDSS versus using the new HSC data.

    \jenny{I suggest removing this here. I do not think it belongs in the Intro:
    Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
    providing appropriate model to describe the \mstar{} distribution of massive 
    galaxy from its center to the very outskirt, we focus on \mstar{} within two 
    different physical apertures in this work:}

%    \begin{itemize}
%    
%        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
%            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
%            builds up the inner, dense core of massive ETGs.  
%            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
%            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
%            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
%            We use \minn{} as a proxy for the mass forged during the ``in-situ''
%            phase. 
%            Given the quality of the HSC data, we can reliably measure \minn{} over our 
%            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
%            0.3 and 0.5).  
%            
%        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
%            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
%            $\times R_{\mathrm{e}}$. 
%            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
%            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
%            ``total'' \mstar{}. 
%            Although not perfect, we argue that our measurements of \mtot{} (which are 
%            actually measuring the light directly out to 100 kpc) are a better tracer 
%            of total \mstar{} than model-dependent results from shallower data 
%            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
%            out to large radii.
%            
%       \end{itemize}}
%% ------------------------------------------------------------------------------------ %%

@@

    We begin by using a broad luminosity cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on \citet{Leauthaud2016}, galaxies with \logms{}$\geq 11.5$ mostly have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
    We therefore select our initial sample to be brighter than 
    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences between 
    the response curves of SDSS-$i$ and HSC-$i$ filters.}
    and also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in the $i$-band.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We further select extended objects with no deblending errors, with well defined 
    centroids, and with \texttt{cModel} magnitudes in all five bands. 
    After removing objects that have pixels affected by saturation, cosmic-rays, or 
    other optical artifacts\footnote{each criterion removes less than 8\% of the 
    entire sample.}. This sample corresponds to 1760845 galaxies and will be referred 
    as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

@@

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
    spec-$z$. Before we can define our mass-complete sample of central galaxies required for 
    our analysis, we describe our one-dimensional photometric analysis (\S \ref{sec:ellipse}) 
    and stellar mass estimations (\S \ref{sec:mstar}). We then define the final sample in \S \ref{sec:final}.
%    By comparing with the Stripe 82 Massive Galaxy Catalog
%    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
%    \mstar{} completeness of the combined BOSS and SDSS samples. 
%    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
%    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
%    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
%    our \texttt{hscZ} sample by 14\%. 
%    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
%    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
%    $10^{12.0}$\msun at $z{\sim} 0.5$. 
%    We can therefore expect our sample to be roughly \mstar{}-complete above 
%    \logms{}$\geq 11.5$-$11.6$. 
%    This question will be addressed more carefully using the overlap region between 
%    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.

%% ------------------------------------------------------------------------------------ %%  
%\subsection{The \redm{}{} cluster catalog}
%    \label{ssec:redmapper}
%    
%    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
%    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
%    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
%    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
%    These authors have developed a well-tested red-sequence cluster finder that has 
%    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
%    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
%    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
%    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
%    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
%    their associated membership probabilities. 
%    Details about the performance of the \redm{}~cluster catalog can be found in 
%    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
%    Several studies have published calibrations between the \redm{}~richness estimate, 
%    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
%    Melchior2016}). 
%    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
%    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
%    The \redm{} catalog therefore helps us group massive central galaxies into 
%    samples with different average \mhalo{}. 
%    We will use the central galaxies of \redm{} clusters 
%    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
%    live in massive halos.
%% ------------------------------------------------------------------------------------ %% 
%
%% ------------------------------------------------------------------------------------ %% 
%  \begin{figure}
%      \centering 
%      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
%      \caption{
%          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
%      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
%      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
%          On average, \mcmodel{} underestimates the total stellar mass of massive 
%          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
%          Vertical histograms indicate the mass difference for galaxies with
%          $11.6<$\logmtot{}$<11.9$. 
%          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
%          function. 
%          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
%          of the total luminosity whereas solid lines correspond to the SMF computed
%          using the total luminosity from our 1-D profile. 
%          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
%          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
%          (red lines).
%          \song{New figure for completeness; Need to update the caption}
%          }
%      \label{fig:mass_complete}
%  \end{figure}

@@

@@

%\subsection{Massive Central Galaxies in Low and High Mass Halos}
%    \label{ssec:mass_central}
%
%    One of the goals of our work is to investigate the halo dependence of the outer 
%    envelope. Although there is a correlation between $M_{\star}$ and $M_{\mathrm{Halo}}$,
%    based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
%    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
%    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
%    With the help of the \redm{} catalog, we can broadly separate our sample into two
%    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
%    live in a fairly broad range of halos masses.
%    
%    % We match this sample with the central galaxies of \redm{}~catalogs using a 
%    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
%    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
%    
%    We match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
%    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
%    galaxies at $0.3 \leq z \leq 0.5$.
%    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
%    as the \rbcg{} sample. 
%    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
%    ${\sim} 41$, corresponding to halo mass of 
%    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
%    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
%    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
%    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
%    %% Saved as "dr1_redbcg_use_sed5b.fits"
%    
%    Out next goal is to construct a sample of central galaxies living in halos with 
%    \logmh{}$<14.0$. 
%    We first identify and remove all galaxies within a cylindrical region around all 
%    \redm{} clusters. 
%    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
%    set to twice the uncertainty of the photometric redshift error. 
%    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
%    \citet{Simet2016} and we use the mass-concentration relation from 
%    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
%    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
%    cluster members.
%    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
%    in our sample will be dominated by central galaxies living in halos with 
%    \logmh{}$\leq 14.0$. 
%    We will refer to this sample of \textbf{central galaxies in less massive halos}
%    as the \nbcg{} sample.
%   
%    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
%    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
%    To ensure a clean separation in \mhalo{}, here we only focus on the central 
%    galaxies of clusters with $\lambda > 30$. 
%    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
%    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
%    We have checked that none of the results in this work depend on the choice of this 
%    $\lambda$ limit. 
%    For massive central galaxies that are not in these cluster-level halos, 
%    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
%    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
%    {\bf I am still a bit confused why stellar mass completeness depends on Mh??}
%
%    We note that at this stage, our \nbcg{} sample still contains galaxies with a 
%    wide range of \mstar{} values. 
%    Later on, once we have more accurate \mstar{} estimates, we will further limit this 
%    sample to \logms{}$ > 11.5$. 
%    At this very high mass end, and given that we have rejected satellites in \redm{} 
%    clusters, any further satellite contamination can be safely neglected 
%    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
%    %% Saved as "dr1_nonbcg_use_sed5b.fits"
%    % TODO: The actual number waits to be updated}
%    
% 
%%% ------------------------------------------------------------------------------------ %%
